Including EW and mixed QCD-EW corrections into PDF fits

### 2020-07-20 paper/sec-pineappl.tex
Add a few corrections to the last commit

If chosen dynamically the Ellis--Sexton scale $Q^2$ depends on the phase space, but we assume the fractions $\xi_\mathrm{R}$ and $\xi_\mathrm{F}$ to be constants of phase space in any case.
This allows variations around the central scale choice $\xi_\mathrm{R} = \xi_\mathrm{F} = 1$, but not changing the scale arbitrarily.
The terms with powers $m > 0$ and $n > 0$ vanish for the central scale choice and are only required for variations of the factorisation and renormalisation scales.
To estimate the perturbative QCD uncertainty---no EW uncertainty is covered by this method---one typically uses a 7-point scale variation, which evaluates the cross section using the following values,
\begin{equation}
(\xi_\mathrm{R}, \xi_\mathrm{F}) \in \left\{ \bigl( 1, 1 \bigr), \bigl( \tfrac{1}{2}, \tfrac{1}{2} \bigr), \bigl( 2, 2 \bigr), \bigl( \tfrac{1}{2}, 1 \bigr), \bigl( 1, \tfrac{1}{2} \bigr), \bigl( 2, 1 \bigr), \bigl( 1, 2 \bigr) \right\} \text{.}
\end{equation}
The (asymmetric) uncertainties are then given as the minimum and maximum value (the envelope), measured from the central value $(1, 1)$.

As is clear from eq.~\eqref{eq:expansion}, the EW coupling $\alpha$ is assumed not to be a dynamically varying coupling, but instead a constant over phase space.
This, however, includes the most common choices of the coupling, which are (not necessarily in this order), $\alpha (0)$, $\alpha (M_\mathrm{Z})$, and $\alpha_{G_\mu}$.

The task that \textsc{PineAPPL} solves can now be described: Approximately reconstruct the functions
\begin{equation}
w_{ab}^{(k,l,m,n,o)} \left( x_1, x_2, Q^2 \right)
\end{equation}
from a set of $N$ function evaluations for specific momentum fractions, scales, and values of the observable:
\begin{equation}
\left\{ x_1^{(i)}, x_2^{(i)}, Q^2_i, \mathcal{O}_i \right\}_{i=1}^N \text{,}
\end{equation}
given by the MC integrator.
Note that in the above equation we do not differentiate w.r.t.\ which phase-space integration (Born, real, subtraction term, etc.) the weight came from, because e.g.\ for a certain NLO all weights are filled into a single grid with fixed $k$ and $l$ and $m=n=0$.

Using eq.~\eqref{eq:expansion} and
\begin{multline}
\frac{\mathrm{d} \sigma}{\mathrm{d} \mathcal{O}} (\mathcal{O}, \xi_\mathrm{R}, \xi_\mathrm{R}) \\
= \sum_{a,b} \int_0^1 \mathrm{d} x_1 \int_0^1 \mathrm{d} x_2 \int_{Q^2_\mathrm{min}}^{Q^2_\mathrm{max}} \mathrm{d} Q^2 \, f_a (x_1, \xi_\mathrm{F}^2 Q^2) f_b (x_2, \xi_\mathrm{F}^2 Q^2) \sigma_{ab} (x_1, x_2, Q^2, \xi_\mathrm{R}, \xi_\mathrm{R}) \text{,}
\label{eq:pineappl-convolution}
\end{multline}
\textsc{PineAPPL} can then quickly calculate hadronic cross sections for arbitrarily many PDF sets and perform scale variations.

>>>>

If chosen dynamically the Ellis--Sexton scale $Q^2$ depends on the phase space, but we assume the fractions $\xi_\mathrm{R}$ and $\xi_\mathrm{F}$ to be constants of phase space in any case.
This allows variations around the central scale choice $\xi_\mathrm{R} = \xi_\mathrm{F} = 1$, but not changing the scale arbitrarily.
The terms with powers $m > 0$ and $n > 0$ vanish for the central scale choice and are only required for variations of the factorisation and renormalisation scales.
To estimate the perturbative QCD uncertainty---no EW uncertainty is covered by this method---one typically uses a 7-point scale variation, which evaluates the cross section using the following values,
\begin{equation}
(\xi_\mathrm{R}, \xi_\mathrm{F}) \in \left\{ \bigl( 1, 1 \bigr), \bigl( \tfrac{1}{2}, \tfrac{1}{2} \bigr), \bigl( 2, 2 \bigr), \bigl( \tfrac{1}{2}, 1 \bigr), \bigl( 1, \tfrac{1}{2} \bigr), \bigl( 2, 1 \bigr), \bigl( 1, 2 \bigr) \right\} \text{.}
\end{equation}
The (asymmetric) uncertainties are then given as the minimum and maximum value (the envelope), measured from the central value $(1, 1)$.
As is clear from eq.~\eqref{eq:expansion}, the EW coupling $\alpha$ is assumed not to be a dynamically varying coupling, but instead a constant over phase space.
This, however, includes the most common choices of the coupling, which are (not necessarily in this order), $\alpha (0)$, $\alpha (M_\mathrm{Z})$, and $\alpha_{G_\mu}$.
The task that \textsc{PineAPPL} solves can now be described: Approximately reconstruct the functions
\begin{equation}
w_{ab}^{(k,l,m,n,o)} \left( x_1, x_2, Q^2 \right)
\end{equation}
from a set of $N$ function evaluations for specific momentum fractions, scales, and values of the observable:
\begin{equation}
\left\{ x_1^{(i)}, x_2^{(i)}, Q^2_i, \mathcal{O}_i \right\}_{i=1}^N \text{,}
\end{equation}
given by the MC integrator.
Using eq.~\eqref{eq:expansion} and
\begin{multline}
\frac{\mathrm{d} \sigma}{\mathrm{d} \mathcal{O}} (\mathcal{O}, \xi_\mathrm{R}, \xi_\mathrm{R}) \\
= \sum_{a,b} \int_0^1 \mathrm{d} x_1 \int_0^1 \mathrm{d} x_2 \int_{Q^2_\mathrm{min}}^{Q^2_\mathrm{max}} \mathrm{d} Q^2 \, f_a (x_1, \xi_\mathrm{F}^2 Q^2) f_b (x_2, \xi_\mathrm{F}^2 Q^2) \sigma_{ab} (x_1, x_2, Q^2, \xi_\mathrm{R}, \xi_\mathrm{R}) \text{,}
\label{eq:pineappl-convolution}
\end{multline}
\textsc{PineAPPL} can then quickly calculate hadronic cross sections for arbitrarily many PDF sets and perform scale variations.

Note that in this section we have omitted the dependence of the weights, observable and scales on the specific kinematics for
which they are computed. Indeed, beyond LO,
different kinematic contributions have to be considered (in ref.~\cite{Bertone:2014zva} they are labelled with an index $\alpha$, see
eq.\ 12 therein). Their consistent treatment must be ensured by the interface between
\textsc{PineAPPL} and the specific cross-section computation at hand\footnote{
    In the FKS subtraction scheme~\cite{Frixione:1995ms,Frixione:1997np} employed in \textsc{mg5\_aMC@NLO}
    maximally one kind of kinematics for each counterterm (soft, collinear, and soft-collinear) is needed, but this
    is not the general case, for example in the Catani--Seymour subtraction~\cite{Catani:1996jh} different dipoles may have different phase spaces and therefore different scales.}.
However, \textsc{PineAPPL} remains completely blind to this fact, as all weights are filled into a given grid
identified only by the indices $k, l, m, n$.
